---
title: "R_code"
output:
  pdf_document: default
  html_document: default
date: "2023-04-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DATA Processing

## Read in data

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(quantmod)
library(readr)
TE <- read.csv("Data/TE_price.csv")
getSymbols("DEXTAUS", src="FRED", from="2000-01-01", to="2022-12-31")
getSymbols("^TWII", src="yahoo", from="2000-01-01", to="2022-12-31")
getSymbols("^GSPC", src="yahoo", from="2000-01-01", to="2022-12-31")

# Subset the data from 2000-01-01 to 2022-12-31
DEXTAUS <- DEXTAUS["2000-01-01/2022-12-31"]


DEXTAUS <- na.omit(DEXTAUS)
GSPC <- na.omit(GSPC)
TWII <- na.omit(TWII)

```

## Convert data type

The `getSymbols()` function from the `quantmod` package returns a time series object of class `xts`. The dates are stored in the index of the object.

```{r}
TE$Date <- as.Date(TE$Date, format = "%m/%d/%Y")
TE <- TE[order(TE$Date),]
TE <- TE[TE$Date>= as.Date("2012-01-01") & TE$Date<= as.Date("2022-12-31"),]
TE <- as.xts(TE)
```


## Summary statistics

```{r}
logEX <- log(DEXTAUS)
dlogEX <- diff(logEX, lag=1, differences=1)
dlogEX <- na.omit(dlogEX)
summary(dlogEX)
mean(dlogEX)
sd(dlogEX)
length(dlogEX)
```

```{r}
logGSPC <- log(GSPC)
dlogGSPC <- diff(logGSPC, lag=1, differences=1)
dlogGSPC <- na.omit(dlogGSPC$GSPC.Close)
summary(dlogGSPC$GSPC.Close)
mean(dlogGSPC$GSPC.Close)
sd(dlogGSPC$GSPC.Close)
length(dlogGSPC$GSPC.Close)
```

```{r}
logTWII <- log(TWII)
dlogTWII <- diff(logTWII, lag=1, differences=1)
dlogTWII <- na.omit(dlogTWII$TWII.Close)
summary(dlogTWII$TWII.Close)
mean(dlogTWII$TWII.Close)
sd(dlogTWII$TWII.Close)
length(dlogTWII$TWII.Close)
```

```{r}
logTE <- log(TE)
dlogTE <- diff(logTE, lag = 1, differences = 1)
dlogTE <- na.omit(dlogTE)
summary(dlogTE)
mean(dlogTE)
sd(dlogTE)
length(dlogTE)
```

# Unit root test


```{r}
library(tseries)
adf.test(dlogEX) # ADF test

adf.test(dlogTE)

adf.test(dlogTWII)

adf.test(dlogGSPC)
```



## Plot of data

```{r, echo=FALSE, results='hide',  message=FALSE, warning=FALSE}
plot(GSPC$GSPC.Close)
dev.copy(png, "Figure/GSPC.png")
dev.off()
```



```{r}
plot(TWII$TWII.Close)
dev.copy(png, "Figure/TWII.png")
dev.off()
```

```{r}
plot(DEXTAUS)
dev.copy(png, "Figure/DEXTAUS.png")
dev.off()
```


```{r}
plot(TE)
dev.copy(png, "Figure/TE.png")
dev.off()

```

## Preparing for regression

Notice that our data have different lengths, which can cause problem when fitting regression.


When you use the `intersect()` function on two vectors of dates, the resulting object is a vector of date-times in `POSIXct` format.
You can use the `as.Date()` or `as.POSIXct()` to convert to readable format.

However, here we have three time series to take intersection.
If you have three `xts` objects and you want to find the intersection of their date ranges, you can use the `Reduce()` function in combination with the `intersect()` function.

```{r}
date_dlogGSPC <- index(dlogGSPC)
date_dlogTWII <- index(dlogTWII)
date_dlogEX <- index(dlogEX)
date_dlogTE <- index(dlogTE)

common_date_TWII <- Reduce(intersect, list(date_dlogEX, date_dlogGSPC, date_dlogTWII)) |> as.Date()
common_date_TE <- Reduce(intersect, list(date_dlogEX, date_dlogGSPC, date_dlogTE)) |> as.Date()
```

```{r}
dlogTWII_common <- dlogTWII[common_date_TWII]
dlogGSPC_common_TWII <- dlogGSPC[common_date_TWII]
x_TWII <- dlogTWII_common-dlogGSPC_common_TWII
y_TWII <- dlogEX[common_date_TWII]
```

```{r}
dlogTE_common <- dlogTE[common_date_TE]
dlogGSPC_common_TE <- dlogGSPC[common_date_TE]
x_TE <- dlogTE_common-dlogGSPC_common_TE
y_TE <- dlogEX[common_date_TE]
```


For convenience, convert into data frame.

```{r}
dlogTWII_common <- data.frame(dlogTWII_common)
dlogGSPC_common_TWII <- data.frame(dlogGSPC_common_TWII)
x_TWII <- data.frame(x_TWII)
y_TWII <- data.frame(y_TWII)


```

```{r}
training_y_TWII <- head(y_TWII, -20)
training_x_TWII <- head(x_TWII,-20)

TWII_train_df <- data.frame(training_y_TWII, training_x_TWII)
```

```{r}
dlogTE_common <- data.frame(dlogTE_common)
dlogGSPC_common_TE <- data.frame(dlogGSPC_common_TE)
x_TE <- data.frame(x_TE)
y_TE <- data.frame(y_TE)
```

```{r}
training_y_TE <- head(y_TE, -20)
training_x_TE <- head(x_TE,-20)

TE_train_df <- data.frame(training_y_TE, training_x_TE)
```


## Preparing for Forecasts

```{r}
testing_y_TWII <- tail(y_TWII, 20)
testing_x_TWII <- tail(x_TWII, 20)

TWII_test_df <- data.frame(testing_y_TWII, testing_x_TWII)
```


```{r}
testing_y_TE <- tail(y_TE, 20)
testing_x_TE <- tail(x_TE, 20)

TE_test_df <- data.frame(testing_y_TE, testing_x_TE)
```


```{r}
# For recovering
logEX_TWII <- logEX[common_date_TWII]
logEX_TE <- logEX[common_date_TE]

logEX_TWII <- data.frame(logEX_TWII)
logEX_TE <- data.frame(logEX_TE)
```


# Estimation

## In-sample regression

```{r}
library(tidyverse)
library(lmtest)
library(sandwich)
```


```{r}
N <- length(TWII_train_df$DEXTAUS)
m <- floor(0.75 * N^(1/3))
reg_TWII <- lm(DEXTAUS~ TWII.Close, data = TWII_train_df)
cat("OLS with Heteroskedasticity and Autocorrelation (HAC) Robust S.E.\n")
hac_se_TWII <- coeftest(reg_TWII, vcov=NeweyWest(reg_TWII, prewhite = F, adjust = T, lag=m-1))
hac_se_TWII

```


```{r}
N <- length(TE_train_df$DEXTAUS)
m <- floor(0.75 * N^(1/3))
reg_TE <- lm(DEXTAUS ~ GSPC.Close, data = TE_train_df)
cat("OLS with Heteroskedasticity and Autocorrelation (HAC) Robust S.E.\n")
hac_se_TE <- coeftest(reg_TE, vcov=NeweyWest(reg_TE, prewhite = F, adjust = T, lag=m-1))
hac_se_TE

```


## Random walk estimation

$y_t=y_{t-1}+w_t$ where $w_t\sim i.i.d.(0,\sigma^2)$

$\implies (1-B)y_t=w_t$

```{r}

lag_training_y_TWII <- lag(training_y_TWII)
# remove the first observation, since it has no lagged value
rw_training_y_TWII <- tail(training_y_TWII, -1)
lag_training_y_TWII <- tail(lag_training_y_TWII, -1)

rw_TWII_train_df <- data.frame(rw_training_y_TWII, lag=lag_training_y_TWII)

rw_TWII <- lm(DEXTAUS~ 0+DEXTAUS.1, data=rw_TWII_train_df)
rw_TWII
```

```{r}
lag_training_y_TE <- lag(training_y_TE)

# remove the first observation, since it has no lagged value
rw_training_y_TE <- tail(training_y_TE, -1)
lag_training_y_TE <- tail(lag_training_y_TE, -1)

rw_TE_train_df <- data.frame(rw_training_y_TE, lag=lag_training_y_TE)

rw_TE <- lm(DEXTAUS~ 0+DEXTAUS.1, data=rw_TE_train_df)
rw_TE
```

```{r}
rw_TWII_arima <- arima(head(y_TWII, -20), order=c(0,1,0))
rw_TWII_arima
```

```{r}
rw_TE_arima <- arima(head(y_TE, -20), order=c(0,1,0))
rw_TE_arima
```

# Forecasting

```{r}
library(forecast)
predict_TWII <- predict(reg_TWII, newdata = TWII_test_df)

# recover the predicted value 
n <- 20
predict_TWII_EX <- predict_TWII + logEX_TWII[(nrow(logEX_TWII)-20+1):nrow(logEX_TWII)-1,]


```




```{r}
predict_TE <- predict(reg_TE, newdata = TE_test_df)
# recover the predicted value 
n <- 20
predict_TE_EX <- predict_TE + logEX_TE[(nrow(logEX_TE)-20+1):nrow(logEX_TE)-1,]


```

## MSE

```{r}
mean((predict_TWII-tail(testing_y_TWII$DEXTAUS, 20))^2)
```

```{r}
mean((predict_TE-tail(testing_y_TE$DEXTAUS, 20))^2)
```

## MSE from Random Walk

```{r}
mean((testing_y_TWII$DEXTAUS)^2)
```

```{r}
mean((testing_y_TE$DEXTAUS)^2)
```


# DM statistics

$d_t=(\hat e_{t+1}^{RW})^2-(\hat e^{SRD}_{t+1})^2$

```{r}
d_TWII <- (testing_y_TWII$DEXTAUS)^2-(predict_TWII-tail(testing_y_TWII$DEXTAUS, 20))^2

d_TE <-(testing_y_TE$DEXTAUS)^2- (predict_TE-tail(testing_y_TE$DEXTAUS, 20))^2
```

```{r}
d_df <- data.frame(d_TWII, d_TE)
d_df
```


```{r}
N <- length(d_TWII)
m <- floor(0.75 * N^(1/3))
reg_d_TWII <- lm(d_TWII~1, data=d_df)
coeftest(reg_d_TWII, vcov=NeweyWest(reg_d_TWII, prewhite = F, adjust=T, lag=m-1))

```

```{r}
N <- length(d_TE)
m <- floor(0.75 * N^(1/3))
reg_d_TE <- lm(d_TE~1, data=d_df)
coeftest(reg_d_TE, vcov=NeweyWest(reg_d_TE, prewhite = F, adjust=T, lag=m-1))
```



